\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{verbatim}

\title{Autonomous Surface Inspection and Adaption on a Mobile Robotics Platform}
\author{Mark Restrepo, Edward Bruce, Ryan Rosenfeld, Will Gerard, Atiena Branch, Gregory Lewin, Nicola Bezzo}
\date{January 2018}

\begin{document}

\section{Abstract}

% Submission of 200-500 word abstracts for contributed papers not previously published or presented. Abstracts should explicitly address the following:

% The design problem being solved
% Background/relevant literature
% Methodological approach developed or adopted
% Preliminary results and implications

Autonomous mobile robots  currently serve a wide array of uses -- from mapping remote locations to planetary exploration. Accurate identification of surfaces and their properties is vital for these robots to achieve optimal performance, as different terrain and surface properties can affect operation. We present a system that classifies unknown surfaces using an unsupervised learning algorithm, and uses this classification to enhance performance on any given surface. Most current solutions to this surface classification problem take a supervised approach, which has several disadvantages. Robots must be trained offline before running, and are unable to adapt to terrains that were not present in the training data. Our approach uses unsupervised learning to identify surfaces the robot has never seen before and adjusts operation for optimal performance on each of them -- without any pre-training whatsoever. Data collected from a LIDAR sensor, 3D Camera, and IMU are combined to create vectors passed to a modified density-based spatial clustering of applications with noise (DBSCAN) algorithm. This algorithm performs online, unsupervised surface classification, learning new surfaces as it travels and storing each surface's ideal operating parameters. The algorithm discards outliers to prevent overfitting. When the robot detects that it has moved onto a new surface it begins learning the optimal traversal parameters to improve the quality of its motion. When it returns to a surface it has seen before, it can quickly adjust its strategy based on the previously learned parameters. The algorithm has been tested on several surfaces with an autonomous ground vehicle. These tests have validated that the algorithm can successfully distinguish between surfaces and adjust the robot's motion for each of them, ensuring the vibrations it experiences don't exceed a predefined threshold. This is accomplished without the use of any a priori training data. This unsupervised learning approach will allow for more robust autonomous operation on unknown surfaces. 

\end{document}

Greg?s comments:

\begin{itemize}
\item Add Bezzo and me as authors. Nicola should be last, since he?s the inspiration behind the work.
\item You focus early on identification of surfaces, but ultimately, your goal is to operate optimally on any given surface. As presented today, this is done as a combination of surface recognition and performance testing. This should be reflected early in the abstract.
\item ?Our approach...?: you should note that you are using an unsupervised approach
\item After ?...new surface...? note that values are stored so that the terrain doesn?t have to be learned again (with an asterisk in the paper that reflects today?s discussion)
\item You need a wrap-up sentence at the end...something to reiterate that this will allow autonomous robots to perform better in unknown environments, for example.
\end{itemize}